Real Estate

### 2023-02-16 src/anchor_city_real_estate.Rmd
output real estate metrics to google sheet
rewriting object names so they are more clear

library(tidyverse)
library(janitor)
library(googlesheets4)
library(DT)
library(MCDA)

city_realEstate_data <- read_sheet("https://docs.google.com/spreadsheets/d/10n55Gt0rySN96OGTQ2_8PzeTcX66n26sOlZBiuiAeBU/edit#gid=808954990")

select_MSAs <- read_sheet("https://docs.google.com/spreadsheets/d/1lmTpSDwVANxdAg5sW87Q8l_gtig7M0EjPPJ6J5_7dwg/edit?usp=sharing")

@@

```{r}
# aggregate yardi data into MSAs by cbsa
city_realEstate_data <- city_realEstate_data %>% 
  clean_names() %>% 
  select(!x7) %>% 
  rename(avg_rent2022 = x2022_rent) %>% 
  rename(occ_rate2021 = percent_occupancy_2021)

@@

anchor_city_data <- city_realEstate_data %>% 
  filter(city %in% c(anchor_cities_list))

@@

>>>>

library(tidyverse)
library(janitor) # clean_names()
library(googlesheets4)
library(DT)

city_occupancy_data <- read_sheet("https://docs.google.com/spreadsheets/d/10n55Gt0rySN96OGTQ2_8PzeTcX66n26sOlZBiuiAeBU/edit#gid=808954990") %>% 
  clean_names() %>% 
  select(!x7) %>% 
  rename(occ_rate2021 = percent_occupancy_2021)

MSA_dempgraphic_data <- read_sheet("https://docs.google.com/spreadsheets/d/1lmTpSDwVANxdAg5sW87Q8l_gtig7M0EjPPJ6J5_7dwg/edit?usp=sharing", sheet = "MSA_demographics")

@@

@@

anchor_city_data <- city_occupancy_data %>% 
  filter(city %in% c(anchor_cities_list))

@@

sheet_write(compliedMSA_realEstate, ss = "https://docs.google.com/spreadsheets/d/1lmTpSDwVANxdAg5sW87Q8l_gtig7M0EjPPJ6J5_7dwg/edit#gid=426650684", sheet = "real_estate_metrics")
